Dynein notes

### 2017-10-30 reorganize/papers/notes/notes.tex
Notes: Add paper about how our model should currently step in the proper direction

@@

\section{Papers}
\subsection{Structure of human cytoplasmic dynein-2 primed for its power stroke}
Schmidt, Carter et al\\

>>>>

\errorstopmode

@@

\section{Papers}
\subsection{Paper on our model stepping in the proper direction given our angle scheme}
Figure 7 of 'Three-dimensional structure of cytoplasmic dynein bound to microtubules' shows a cartoon interpretation of a dynein-MT crystal structure indicating that a model which has its tail-load towards the + end will step towards the - end of the MT.\\

\subsection{Structure of human cytoplasmic dynein-2 primed for its power stroke}
Schmidt, Carter et al\\
